\begin{thebibliography}{99}
\pagestyle{empty}

\phantomsection
\addcontentsline{toc}{section}{\refname}

\bibitem{bib3}
Shkuratjana N., Shevchuk S. (2010) Modern Ukrainian literary language Modular course [Suchasnaukrayins`ka
literaturnamova Modul`ny`jkurs] Kyiv: Arij, p 824.

\bibitem{bib5}
Constituency Grammars : URL :
https://web.stanford.edu/~jurafsky/slp3/12.pdf

\bibitem{bib6}
Cocke, J., \& Schwartz, J. T. (1970). Programming languages and their compilers. Preliminary notes. Courant Inst, of Math. Sciences, New York University.

\bibitem{bib7}
Chomsky, N. (1959). On certain formal properties of grammars. Information and control, 2(2), 137-167. : doi : https://doi.org/10.1016\%2FS0019-9958\%2859\%2990362-6

\bibitem{bib8}
Logical Representations of Sentence Meaning : URL :
https://web.stanford.edu/~jurafsky/slp3/15.pdf

\bibitem{bib1}
Marie-Catherine de Marneffe, Christopher D. Manning, Joakim Nivre, Daniel Zeman;
Universal Dependencies. Computational Linguistics 2021; 47 (2): 255–308. doi:
https://doi.org/10.1162/coli\_a\_00402

\bibitem{bib2}
Nivre, J., de Marneffe, M.-C., Ginter, F., Hajič, J., Manning, C. D., Pyysalo, S., Schuster, S., Tyers, F., \& Zeman, D. (2020). Universal Dependencies v2: An Evergrowing Multilingual Treebank Collection. Proceedings of the 12th Language Resources and Evaluation Conference, 4034–4043. URL: https://aclanthology.org/2020.lrec-1.497

\bibitem{bib9}
Lipenkova, J., \& Souček, M. (2014, April). Converting Russian dependency treebank to Stanford typed dependencies representation. In Proceedings of the 14th Conference of the European Chapter of the Association for Computational Linguistics, volume 2: Short Papers (pp. 143-147).

\bibitem{bib10}
Nivre, J. (2007, June). Data-driven dependency parsing across languages and domains: perspectives from the CoNLL-2007 shared task. In Proceedings of the Tenth International Conference on Parsing Technologies (pp. 168-170).

\bibitem{bib11}
Buchholz, S., \& Marsi, E. (2006, June). CoNLL-X shared task on multilingual dependency parsing. In Proceedings of the tenth conference on computational natural language learning (CoNLL-X) (pp. 149-164).

\bibitem{bib4}
Language Server Protocol : URL :
https://microsoft.github.io/language-server-protocol

\bibitem{bib12}
Золотий морфосинтаксовий стандарт : URL :
https://mova.institute/золотий\_стандарт



\bibitem{bib13}
Scott Chacon, Ben Straub, Pro Git : Apress; 2nd ed. edition 2014. 440p.

\bibitem{bib14}
Gabriel Valiente Algorithms on Trees and Graphs : Springer; 2002nd edition (September 5, 2002). 450p.

\bibitem{bib15}
Маккинли У. Python и анализ данных : ДМК Пресс, 2015. 482с.

\bibitem{bib16}
Lundh F. Python Standard Library : O’Reilly \& Associates, 2001. 254p.

\bibitem{bib17}
Dynamic Programming on Trees (Algorithms for Coding Interviews), 2022. 141p.

\bibitem{bib18}
Universal Dependencies : URL : https://universaldependencies.org

\bibitem{bib19}
CoNLL-U Viewer : URL : https://universaldependencies.org/conllu\_viewer.html

\bibitem{bib20}
Pandas : URL : https://pandas.pydata.org

\bibitem{bib21}
Numpy : URL : https://numpy.org


\end{thebibliography}